Kelompok 4_Praktikum_Pekan 8

### 2024-04-08 Project/Kelompok 4_Praktikum_Pekan 8.Rmd
Update

```{r fig.height=6.5, fig.width=30, dpi=300}
set.seed(361)
mix_data_1 <- lapply(seq_along(sample_sizes), function(i) {
  n <- sample_sizes[i]
  norm_part <- matrix(rnorm(n*k/2, mean = 0, sd = 1), k/2)
  chisq_part <- matrix(rchisq(n *k /2, df =5), k /2)
  rbind(norm_part, chisq_part)
})

par(mfrow = c(1, 5))
hist(mix_data_1[[1]], main = "Sebaran Campuran 1\nUkuran sample (n=4)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#eae1f8")
hist(mix_data_1[[2]], main = "Sebaran Campuran 1\nUkuran sample (n=12)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#d5bbf3")
hist(mix_data_1[[3]], main = "Sebaran Campuran 1\nUkuran sample (n=20)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#9d48c7")
hist(mix_data_1[[4]], main = "Sebaran Campuran 1\nUkuran sample (n=60)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")
hist(mix_data_1[[5]], main = "Sebaran Campuran 1\nUkuran sample (n=100)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#48185b")
```

@@

```{r fig.height=6.5, fig.width=30, dpi=300}
set.seed(361)
mix_data_2 <- lapply(sample_sizes, function(n) {
  chisq_a <- matrix(rchisq(n*k/2, df = 3), k/2)
  chisq_b <- matrix(rchisq(n*k/2, df = 8), k/2)
  rbind(chisq_a, chisq_b)
})

par(mfrow = c(1, 5))
hist(mix_data_2[[1]], 
     main = "Sebaran Campuran 2\nUkuran sample (n=4)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#fae7fd")
hist(mix_data_2[[2]], 
     main = "Sebaran Campuran 2\nUkuran sample (n=12)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#eb91f2")
hist(mix_data_2[[3]], 
     main = "Sebaran Campuran 2\nUkuran sample (n=20)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#e44cb5")
hist(mix_data_2[[4]], 
     main = "Sebaran Campuran 2\nUkuran sample (n=60)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#96336c")
hist(mix_data_2[[5]], 
     main = "Sebaran Campuran 2\nUkuran sample (n=100)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#61283f")
```

>>>>

```{r fig.height=5, fig.width=15, dpi=300}
k <- 1000; n <- 1
mix_data_1 <- rbind(matrix(rnorm(n*k/2, mean = 0, sd = 1), k/2), 
                    matrix(rchisq(n *k /2, df =5), k /2))
hist(mix_data_1, main = "Sebaran Populasi Campuran 1", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")
```

```{r fig.height=6.5, fig.width=30, dpi=300}
set.seed(361)
k <- 1000

mean_dist <- function(dist, n){
  means <- rep(NA, k) 
  for (i in c(1:k)) 
       means[i] <- mean(sample(dist, size = n, replace = FALSE)) 
  return(means)
}

mixed_data1 <- lapply(sample_sizes, function(n) mean_dist(mix_data_1, n))

par(mfrow = c(1, 5))
hist(mixed_data1[[1]], main = "Sebaran Campuran 1\nUkuran sample (n=4)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#eae1f8")
hist(mixed_data1[[2]], main = "Sebaran Campuran 2\nUkuran sample (n=12)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#d5bbf3")
hist(mixed_data1[[3]], main = "Sebaran Campuran 3\nUkuran sample (n=20)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#9d48c7")
hist(mixed_data1[[4]], main = "Sebaran Campuran 4\nUkuran sample (n=60)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#792b9a")
hist(mixed_data1[[5]], main = "Sebaran Campuran 5\nUkuran sample (n=100)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#48185b")
```

@@

```{r fig.height=5, fig.width=15, dpi=300}
k <- 1000; n <- 1
mix_data_2 <- rbind(matrix(rchisq(n*k/2, df = 3), k/2), 
                    matrix(rchisq(n*k/2, df = 8), k/2))
hist(mix_data_2, main = "Sebaran Populasi Campuran 2", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#96336c")
```

```{r fig.height=6.5, fig.width=30, dpi=300}
set.seed(361)

mixed_data2 <- lapply(sample_sizes, function(n) mean_dist(mix_data_2, n))

par(mfrow = c(1, 5))
hist(mixed_data2[[1]], main = "Sebaran Campuran 1\nUkuran sample (n=4)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#fae7fd")
hist(mixed_data2[[2]], main = "Sebaran Campuran 2\nUkuran sample (n=12)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#eb91f2")
hist(mixed_data2[[3]], main = "Sebaran Campuran 3\nUkuran sample (n=20)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#e44cb5")
hist(mixed_data2[[4]], main = "Sebaran Campuran 4\nUkuran sample (n=60)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#96336c")
hist(mixed_data2[[5]], main = "Sebaran Campuran 5\nUkuran sample (n=100)", 
     xlab = "Nilai", ylab = "Frekuensi", col = "#61283f")
```
